borrow-lambda

### 2025-04-20 paper/paper.tex
finish last todo

\texttt{TODO: maybe add example code, explanation for functions polymorphic over lifetimes}

>>>>

Lastly, functions that accept references as input, and return references, need to
ensure that these references have a scope that is larger than the function itself.
However, the scope that these references have need not be fixed - they just need
to be sufficiently large. As a result, functions are actually polymorphic over
lifetime variables, provided that the instantiation lifetime variable meets
the constraints we have discussed. Figure \ref{lfpolyex} shows an example.
\begin{figure}[h]
    \begin{lstlisting}
        fn main() {
            let n = 0;
            let my_ref = borrower(&n);
        }

        fn borrower<'a>(r: &'a u32) -> &'a u32 {
            let b = 0;
            &b // error: variable 'b' does not live long enough 
        }
    \end{lstlisting}
    \caption{Example of a function with a polymorphic lifetime variable}
    \label{lfpolyex}
\end{figure}
The function \texttt{borrower} requires that the reference passed in, and the
reference returned out, has a lifetime \texttt{'a}. When the function is called,
this variable \texttt{'a} is instantiated to the lifetime of the reference that
is passed in, that being \texttt{\&n}. Thus, the typechecker can determine that
the implementation of the function is invalid, as the reference \texttt{\&b} is
being returned out of the function, but has a lifetime smaller than the lifetime
of \texttt{\&n}, which is what \texttt{'a} was instantiated to.
